\documentclass[a4paper,12pt,final]{extreport}
\usepackage[%
    left=0.50in,%
    right=0.50in,%
    top=0.50in,%
    bottom=1.0in,%
    paperheight=11in,%
    paperwidth=8.5in%
]{geometry}%
\usepackage{geometry}
\usepackage{adjustbox}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{fontspec}
\newcounter{tottables}
\usepackage{xltxtra} 
\setcounter{secnumdepth}{0}
\renewcommand\theadalign{bc}
\renewcommand\theadfont{\bfseries}
\renewcommand\theadgape{\Gape[4pt]}
\renewcommand\cellgape{\Gape[4pt]}
\pagenumbering{gobble}

\begin{document}
\section{Taras Shevchenko}
\subsection{Executive summary}
\begin{enumerate}
  \item Performance oriented design of applications.
  \item Strong understanding of algorithms, networking, systems architecture and end-user experience.
  \item Programming in the Linux environment (user space).
  \item Strong in-depth skills in STL, C++, Python, general-purpose algorithms and generic programming.
  \item Understanding of low-level details related to compilers, interpreters and column-store databases.
  \item In-breadth and in-depth understanding of Open Source software facilities.
\end{enumerate}

\subsection{The last industrial experience}
\subsubsection{Key activities and achievements at Rails Reactor (Since 2016)}
\begin{itemize}
  \item Negotiations with clients.
  \item Implemented a few client-side and server-side API in different programming languages for e-commerce services.
  \item Applied Guided Local Search algorithm for solving advanced modification
        of the Vehicle Routing Problem and implemented a related application
        for end users.
  \item Created Machine Learning algorithm for Ideal Customer Profile evaluation.
  \item Implemented in React a cross-browser extension for selling products.
\end{itemize}

\subsection{Education}
\begin{tabular}
{|c | c | c| c|}
\hline
\thead{Institution} & \thead{Degree} & \thead{Specialization} & \thead{Thesis} \\
\hline
\multirow{3}{*}{
\makecell{
Institute for Applied\\
System Analysis at NTUU \\
Kyiv Polytechnic Institute
}
} & \makecell{Master's} & \makecell{System Analysis and \\ Control Theory} & \makecell{Multimodal Search System\\ ~}\\
                \cline{2-4}
  & \makecell{Bachelor's} & \makecell{Artificial Intelligence} & \makecell{Distributed Search Relevance Evaluation\\ ~ } \\
\hline
\end{tabular}
\subsection{Other information and activities}
\begin{itemize}
  \item Solid background in Mathematics.
  \item Production experience with at least 6 programming languages.
  \item ACM ICPC 2017 semifinalist.
\end{itemize}
\subsection{Contacts}
\begin{tabular}
{c  c  c c  c c  c c}
\thead{Github:} & \href{https://github.com/tshev}{tshev} &
\thead{Skype:}  & tshev.com &
\thead{LinkedIn:} & \href{http://bit.ly/1SblWF4}{Taras Shevchenko} &
\thead{Location:} & Kyiv, Ukraine
\end{tabular}
\end{document}
